Logarithmic Space Verifiers on NP-complete

### 2019-11-13 doc/manuscript.tex
Updated the content proof

\section{Materials and Methods}

\subsection{Preliminaries}

@@

\subsection{Hypothesis}

@@

\subsection{Consequences}

@@

\begin{theorem}
\label{closed}
If $T(n)$ is such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
and is not a constant, then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ that is not a constant when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes at most $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way. The existence of such function $G(n) > 1$ is possible because the family of languages $\textit{1TAPE}[T'(n)]$ is a subset of $P$ and thus $G(n) < 2^{n}$ \cite{Pap03}. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$. However, we know in that instance of size at most $G(n) \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right. Therefore, the instance of size at most $G(n) \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with at most $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language. In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ has a projection to the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$. Recursively, we obtain that the family of languages of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ has a projection to the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)^{2}})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. Consequently, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)^{2}})]$. If we recursively continue so forth, then we obtain that the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)^{j}})]$ for every natural number $j$. However, if we follow this assumption, then we obtain that
\[\lim_{j\to\infty} T'(\frac{n}{G(n)^{j}}) = T'(0)\]
has a cardinality greater than or equal to $\textit{1TAPE}[T'(n)]$. Nevertheless, the cardinality of the family of languages $\textit{1TAPE}[T'(n)]$ cannot be lesser than or equal to the cardinality of family of languages $\textit{1TAPE}[T'(0)]$ just assuming that $T'(n)$ is not a constant. Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every sparse function $T(n)$ when $T(n)$ is not a constant.
\end{proof}

@@

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. We can extend this result when $T(n)$ is not a constant \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}

@@

\subsection{Programming Codes}

>>>>

\section{Preliminaries}

@@

\section{Hypothesis}

@@

\section{Consequences}

@@

\begin{theorem}
\label{closed}
If $T(n)$ is such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes at most $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $G(n) \times n$ symbols for some function $G(n) > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way. The existence of such function $G(n) > 1$ is possible because the family of languages $\textit{1TAPE}[T'(n)]$ is a subset of $P$ and thus $G(n) < 2^{n}$ \cite{Pap03}. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $G(n) \times n$.

However, we know in that instance of size at most $G(n) \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right. Therefore, the instance of size at most $G(n) \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with at most $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language.

In this way, we obtain that the languages in $\textit{1TAPE}[T'(n)]$ have a projection to the languages in $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ for some function $G(n) > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$. However, we already know that $\textit{1TAPE}[T'(\frac{n}{G(n)})] \subseteq \textit{1TAPE}[T'(n)]$ and thus, if the cardinality of $\textit{1TAPE}[T'(n)]$ is lesser than or equal to the cardinality of $\textit{1TAPE}[T'(\frac{n}{G(n)})]$, then we have that $\textit{1TAPE}[T'(\frac{n}{G(n)})] = \textit{1TAPE}[T'(n)]$. Nevertheless, we know that the family of languages $\textit{1TAPE}[T'(\frac{n}{G(n)})]$ cannot be equal to the family of languages $\textit{1TAPE}[T'(n)]$ for some function $G(n) > 1$. Therefore, we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every function $T(n)$ with small amount of work tape.
\end{proof}

@@

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. Hence, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}

@@

\section{Codes}
